Gammapy: A Python package for gamma-ray astronomy

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

Finally, to limit other sources of systematic uncertainties, a data validity
domain is determined by the \code{SafeMaskMaker}. It can be used to limit the
extent of the field of view used or to limit the energy range to e.g., a domain
where the energy reconstruction bias is below a given value.

@@

\begin{itemize}
	\item \code{SpectralModel}: models to describe spectral shapes of sources
	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources
	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
	      light and phase curves
\end{itemize}

>>>>

Finally, to limit other sources of systematic uncertainties, a data validity
domain is determined by the \code{SafeMaskMaker}. It can be used to limit the
extent of the field of view used or to limit the energy range to, e.g., a domain
where the energy reconstruction bias is below a given value.

@@

\begin{itemize}
	\item \code{SpectralModel}: models to describe spectral shapes of sources,
	\item \code{SpatialModel}: models to describe spatial shapes (morphologies) of sources
	\item \code{TemporalModel}: models to describe temporal flux evolution of sources, such as
	      light and phase curves
\end{itemize}
